BSTERGM: Bayesian Separable-Temporal Exponential family Graph Models

### 2020-12-10 doc/doc.tex
tex 1211 0420

Moreover, we already have a generative algorithm for a network at the specific parameter point.
In fact, it is same to the algorithm used in the auxiliary chain.
Thus, we can predict the form of network at $T+1,T+2,...$ using posterior sample following the standard Bayesian prediction method.
For example, for predicting networks structure at $T+1$,
\begin{itemize}
    \item Run K iteration using auxiliary chain at $y_T$ with each posterior sample points.
    \item Take the each network as a predicted result.
\end{itemize}
If you need, calculate some network statistics of the generated networks and get some summary statistics on them.

@@

Finally, I append the results of goodness of fit.

>>>>

The interpretation of the parameter is very easy because of the separated formation and dissolution model.
Since we cannot know the normalizing constant in the models, but we get an odds very easily from the model definition.
And, from parameter value, we can expect the direction or tendency of network structure with high probability.
If $\theta^+$ is higher, a network with high $s$ have high probability at the formation model, and vice versa.
Likewise, If $\theta^-$ is lower, a network with lower $s$ have high probability at the dissolution model, and vice versa.
Thus, if $\theta^+$ go to $-\infty$ and $\theta^-$ go to $\infty$, the network does not change easily over time.
If $\theta^+$ go to $\infty$ and $\theta^-$ go to $-\infty$, the network changes drastically over time.
If $\theta^+$ go to $\infty$ and $\theta^-$ go to $\infty$, the network becomes denser over time.
Finally, if $\theta^+$ go to $-\infty$ and $\theta^-$ go to $-\infty$, the network becomes sparser over time.

Let us turn to the prediction method. 
we already have a generative algorithm for a network at the specific parameter point.
In fact, it is same to the algorithm used in the auxiliary chain.
Thus, we can predict the form of network at $T+1,T+2,...$ using posterior sample following the standard Bayesian prediction method.
For example, for predicting networks structure at $T+1$,
\begin{itemize}
    \item Run K iteration using auxiliary chain at $y_T$ with each posterior sample points.
    \item Take the each network as a predicted result.
\end{itemize}
If you need, calculate some network statistics of the generated networks and get some summary statistics on them.

@@

Finally, I append the results of goodness of fit.
Compare observed (true) value with quantiles of simulated values of parts of sufficient network statistics,
generated by the goodness of fit algorithm.
Since this example has simply just two edge terms, and since the BSTERGMs share same parameter
for each network statistics but values of network statistics are different at each time point,
the sufficient statistics do not fitted perfectly to observed networks' values.
However, the tendency of simulated values goes with the observed values.

\begin{table}[h!]
    \centering
        \begin{tabular}{c| c | c | c | c |c |c |c |c }
            Sequence& timelag & netstat & obs & q0.1 & q0.25 & q0.5 & q0.75 & q0.9 \\
            \hline \hline
            1 & 1-2 & $D_0$ & 4 &  0& 0& 0& 1& 1 \\
            1 & 1-2 & $D_1$ & 1 &  0& 0& 1& 2& 3 \\
            1 & 1-2 & $D_2$ & 0 &  1& 1& 2& 3& 4 \\
            1 & 1-2 & $D_3$ & 3 &  1& 2& 3& 4& 5 \\
            1 & 1-2 & $D_4$ & 1 &  1& 2& 3& 4& 6 \\
            1 & 1-2 & $D_5$ & 3 &  2& 3& 4& 5& 7 \\
            1 & 1-2 & $D_6$ & 3 &  2& 3& 5& 6& 8 \\
            1 & 1-2 & $D_7$ & 5 &  3& 4& 5& 7& 9 \\
            1 & 1-2 & $D_8$ & 9 &  3& 4& 6& 7& 9 \\
            1 & 1-2 & $D_9$ & 5 &  3& 4& 6& 7& 9 \\
            1 & 1-2 & $D_{10}$ & 4 &  2& 3& 5& 6& 8 \\
            1 & 1-2 & $D_{11}$ & 4 &  1& 2& 4& 5& 6 \\
            1 & 1-2 & $D_{12}$ & 4 &  0& 1& 2& 3& 5 \\
            1 & 1-2 & $D_{13}$ & 2 &  0& 1& 1& 2& 3 \\
            1 & 1-2 & $D_{14}$ & 1 &  0& 0& 1& 1& 2 \\
            1 & 1-2 & $D_{15}$ & 0 &  0& 0& 0& 1& 2 \\
            1 & 1-2 & $P_0$ & 8 &  25& 28& 33& 37& 42 \\
            1 & 1-2 & $P_1$ & 10 & 29& 33& 38& 43& 48 \\
            1 & 1-2 & $P_2$ & 29 & 30& 33& 38& 43& 47 \\
            1 & 1-2 & $P_3$ & 27 & 28& 32& 36& 40& 44 \\
            1 & 1-2 & $P_4$ & 13 & 19& 23& 28& 32& 37 \\
            1 & 1-2 & $P_5$ & 37 &  9& 13& 17& 22& 26 \\
            1 & 1-2 & $P_6$ & 40 &  3& 5& 8& 11& 15 \\
            1 & 1-2 & $P_7$ & 20 &  3& 4& 5& 7& 9 \\
            1 & 1-2 & $P_8$ & 20 &  0& 1& 3& 5& 7 \\
            1 & 1-2 & $|y_2|$ & 212 &  186& 194& 204& 214& 223 \\
        \end{tabular}
        \caption{GOF: sequence 1 (1)}
        % \label{tab:data}
    \end{table}
\clearpage
\begin{table}[h!]
    \centering
        \begin{tabular}{c| c | c | c | c |c |c |c |c }
            Sequence& timelag & netstat & obs & q0.1 & q0.25 & q0.5 & q0.75 & q0.9 \\
            \hline \hline
            1 & 2-3 & $D_0$ & 5 &  0& 0& 0& 0& 1 \\
            1 & 2-3 & $D_1$ & 0 &  0& 0& 0& 1& 2 \\
            1 & 2-3 & $D_2$ & 2 &  0& 0& 1& 2& 2 \\
            1 & 2-3 & $D_3$ & 1 &  0& 1& 2& 2& 3 \\
            1 & 2-3 & $D_4$ & 2 &  1& 1& 2& 3& 4 \\
            1 & 2-3 & $D_5$ & 5 &  1& 2& 3& 4& 5 \\
            1 & 2-3 & $D_6$ & 2 &  1& 3& 4& 5& 7 \\
            1 & 2-3 & $D_7$ & 3 &  2& 4& 5& 7& 8 \\
            1 & 2-3 & $D_8$ & 8 &  3& 4& 6& 7& 8 \\
            1 & 2-3 & $D_9$ & 4 &  3& 5& 6& 8& 9 \\
            1 & 2-3 & $D_{10}$ & 4 &  3& 4& 5& 7& 9 \\
            1 & 2-3 & $D_{11}$ & 5 &  2& 3& 5& 6& 8 \\
            1 & 2-3 & $D_{12}$ & 1 &  1& 2& 4& 5& 6 \\
            1 & 2-3 & $D_{13}$ & 3 &  1& 2& 2& 4& 5 \\
            1 & 2-3 & $D_{14}$ & 0 &  0& 1& 2& 3& 4 \\
            1 & 2-3 & $D_{15}$ & 1 &  0& 0& 1& 2& 3 \\
            1 & 2-3 & $P_0$ & 11 & 20& 24& 28& 32& 37 \\
            1 & 2-3 & $P_1$ & 12 & 32& 36& 41& 47& 51 \\
            1 & 2-3 & $P_2$ & 23 & 35& 39& 44& 49& 53 \\
            1 & 2-3 & $P_3$ & 52 & 32& 35& 40& 45& 49 \\
            1 & 2-3 & $P_4$ & 39 & 24& 28& 33& 37& 42 \\
            1 & 2-3 & $P_5$ & 24 & 13& 18& 22& 27& 32 \\
            1 & 2-3 & $P_6$ & 21 &  6& 9& 12& 17& 21 \\
            1 & 2-3 & $P_7$ & 20 &  2& 3& 5& 8& 12 \\
            1 & 2-3 & $P_8$ & 13 &  0& 1& 2& 4& 6 \\
            1 & 2-3 & $|y_3|$ & 227 &  213& 222& 232& 243& 253 \\
        \end{tabular}
        \caption{GOF: sequence 1 (2)}
        % \label{tab:data}
    \end{table}
\clearpage

\begin{table}[h!]
    \centering
        \begin{tabular}{c| c | c | c | c |c |c |c |c }
            Sequence& timelag & netstat & obs & q0.1 & q0.25 & q0.5 & q0.75 & q0.9 \\
            \hline \hline
            2 & 1-2 & $D_0$ & 3 &  0& 0& 0& 0& 0 \\
            2 & 1-2 & $D_1$ & 2 &  0& 0& 0& 0& 0 \\
            2 & 1-2 & $D_2$ & 4 &  0& 0& 0& 0& 1 \\
            2 & 1-2 & $D_3$ & 1 &  0& 0& 0& 1& 1 \\
            2 & 1-2 & $D_4$ & 3 &  0& 0& 1& 1& 2 \\
            2 & 1-2 & $D_5$ & 0 &  0& 0& 1& 2& 3 \\
            2 & 1-2 & $D_6$ & 0 &  0& 1& 2& 3& 4 \\
            2 & 1-2 & $D_7$ & 1 &  0& 1& 2& 3& 4 \\
            2 & 1-2 & $D_8$ & 4 &  1& 1& 2& 4& 5 \\
            2 & 1-2 & $D_9$ & 1 &  1& 1& 2& 3& 5 \\
            2 & 1-2 & $D_{10}$ & 3 &  1& 2& 3& 4& 5 \\
            2 & 1-2 & $D_{11}$ & 1 &  1& 2& 2& 4& 5 \\
            2 & 1-2 & $D_{12}$ & 1 &  1& 2& 3& 4& 5 \\
            2 & 1-2 & $D_{13}$ & 2 &  1& 2& 3& 4& 5 \\
            2 & 1-2 & $D_{14}$ & 3 &  1& 2& 3& 4& 5 \\
            2 & 1-2 & $D_{15}$ & 1 &  1& 2& 3& 4& 6 \\
            2 & 1-2 & $D_{16}$ & 1 &  1& 2& 3& 4& 6 \\
            2 & 1-2 & $D_{17}$ & 3 &  1& 2& 2& 4& 6 \\
            2 & 1-2 & $D_{18}$ & 2 &  1& 2& 3& 4& 6 \\
            2 & 1-2 & $D_{19}$ & 2 &  1& 2& 3& 4& 5 \\
            2 & 1-2 & $D_{20}$ & 2 &  1& 2& 3& 4& 5 \\
            2 & 1-2 & $D_{21}$ & 2 &  0& 1& 2& 3& 4 \\
            2 & 1-2 & $P_4$ & 21 & 33& 38& 43& 48& 52 \\
            2 & 1-2 & $P_5$ & 28 & 35& 38& 43& 48& 54 \\
            2 & 1-2 & $P_6$ & 31 & 33& 37& 42& 47& 52 \\
            2 & 1-2 & $P_7$ & 31 & 28& 32& 37& 43& 48 \\
            2 & 1-2 & $P_8$ & 32 & 21& 25& 31& 36& 41 \\
            2 & 1-2 & $P_9$ & 23 & 14& 18& 23& 29& 33 \\
            2 & 1-2 & $P_{10}$ & 27 & 8& 12& 16& 21& 26 \\
            2 & 1-2 & $P_{11}$ & 21 & 4& 7& 10& 14& 19 \\
            2 & 1-2 & $|y_2|$ & 342 &  344& 356& 370& 387& 400 \\
        \end{tabular}
        \caption{GOF: sequence 2 (1)}
        % \label{tab:data}
    \end{table}
\clearpage
\begin{table}[h!]
    \centering
        \begin{tabular}{c| c | c | c | c |c |c |c |c }
            Sequence& timelag & netstat & obs & q0.1 & q0.25 & q0.5 & q0.75 & q0.9 \\
            \hline \hline
            2 & 2-3 & $D_0$ & 0 &  0& 0& 0& 0& 0 \\
            2 & 2-3 & $D_1$ & 3 &  0& 0& 0& 0& 0 \\
            2 & 2-3 & $D_2$ & 1 &  0& 0& 0& 0& 0 \\
            2 & 2-3 & $D_3$ & 2 &  0& 0& 0& 0& 1 \\
            2 & 2-3 & $D_4$ & 2 &  0& 0& 0& 1& 2 \\
            2 & 2-3 & $D_5$ & 1 &  0& 0& 1& 1& 2 \\
            2 & 2-3 & $D_6$ & 1 &  0& 0& 1& 2& 3 \\
            2 & 2-3 & $D_7$ & 2 &  0& 1& 2& 3& 4 \\
            2 & 2-3 & $D_8$ & 1 &  1& 1& 2& 3& 4 \\
            2 & 2-3 & $D_9$ & 1 &  1& 1& 2& 3& 5 \\
            2 & 2-3 & $D_{10}$ & 3 &  1& 2& 3& 4& 5 \\
            2 & 2-3 & $D_{11}$ & 2 &  1& 1& 2& 4& 5 \\
            2 & 2-3 & $D_{12}$ & 2 &  1& 2& 4& 5& 6 \\
            2 & 2-3 & $D_{13}$ & 3 &  1& 2& 3& 4& 5 \\
            2 & 2-3 & $D_{14}$ & 2 &  1& 2& 3& 4& 5 \\
            2 & 2-3 & $D_{15}$ & 0 &  1& 2& 3& 4& 5 \\
            2 & 2-3 & $D_{16}$ & 3 &  1& 2& 3& 4& 5 \\
            2 & 2-3 & $D_{17}$ & 1 &  1& 2& 2& 4& 5 \\
            2 & 2-3 & $D_{18}$ & 0 &  1& 2& 3& 4& 5 \\
            2 & 2-3 & $D_{19}$ & 3 &  1& 2& 3& 4& 5 \\
            2 & 2-3 & $D_{20}$ & 2 &  1& 2& 3& 4& 5 \\
            2 & 2-3 & $D_{21}$ & 0 &  1& 1& 2& 3& 4 \\
            2 & 2-3 & $P_4$ & 6 & 35& 29& 44& 48& 53 \\
            2 & 2-3 & $P_5$ & 27 & 34& 38& 42& 48& 53 \\
            2 & 2-3 & $P_6$ & 34 & 35& 39& 44& 49& 53 \\
            2 & 2-3 & $P_7$ & 25 & 33& 36& 41& 46& 50 \\
            2 & 2-3 & $P_8$ & 27 & 28& 32& 27& 42& 47 \\
            2 & 2-3 & $P_9$ & 39 & 22& 26& 31& 36& 40 \\
            2 & 2-3 & $P_{10}$ & 24 & 15& 19& 24& 29& 34 \\
            2 & 2-3 & $P_{11}$ & 27 & 10& 14& 18& 23& 27 \\
            2 & 2-3 & $|y_3|$ & 433 &  375& 387& 402& 417& 430 \\
        \end{tabular}
        \caption{GOF: sequence 2 (2)}
        % \label{tab:data}
    \end{table}
\clearpage

\begin{table}[h!]
    \centering
        \begin{tabular}{c| c | c | c | c |c |c |c |c }
            Sequence& timelag & netstat & obs & q0.1 & q0.25 & q0.5 & q0.75 & q0.9 \\
            \hline \hline
            3 & 1-2 & $D_0$ & 4 &  0& 0& 0& 1& 2 \\
            3 & 1-2 & $D_1$ & 4 &  6& 7& 8& 9& 10 \\
            3 & 1-2 & $D_2$ & 3 &  1& 2& 3& 4& 5 \\
            3 & 1-2 & $D_3$ & 1 &  0& 0& 1& 1& 2 \\
            3 & 1-2 & $D_4$ & 2 &  0& 1& 1& 2& 3 \\
            3 & 1-2 & $D_5$ & 7 &  1& 2& 3& 4& 5 \\
            3 & 1-2 & $D_6$ & 4 &  3& 4& 5& 7& 8 \\
            3 & 1-2 & $D_7$ & 3 &  3& 4& 5& 6& 7 \\
            3 & 1-2 & $D_8$ & 4 &  2& 3& 4& 5& 6 \\
            3 & 1-2 & $D_9$ & 6 &  2& 3& 4& 5& 6 \\
            3 & 1-2 & $D_{10}$ & 0 &  2& 3& 4& 5& 6 \\
            3 & 1-2 & $D_{11}$ & 6 &  2& 3& 4& 5& 6 \\
            3 & 1-2 & $D_{12}$ & 2 &  1& 1& 2& 3& 4 \\
            3 & 1-2 & $D_{13}$ & 1 &  0& 1& 1& 2& 3 \\
            3 & 1-2 & $D_{14}$ & 0 &  0& 1& 1& 2& 3 \\
            3 & 1-2 & $D_{15}$ & 0 &  0& 0& 1& 1& 2 \\
            3 & 1-2 & $P_0$ & 7 & 9& 10& 12& 13& 14 \\
            3 & 1-2 & $P_1$ & 22 & 12& 14& 17& 20& 23 \\
            3 & 1-2 & $P_2$ & 21 & 15& 18& 21& 24& 27 \\
            3 & 1-2 & $P_3$ & 42 & 23& 27& 30& 34& 37 \\
            3 & 1-2 & $P_4$ & 24 & 25& 29& 32& 36& 40 \\
            3 & 1-2 & $P_5$ & 32 & 22& 25& 29& 33& 37 \\
            3 & 1-2 & $P_6$ & 14 & 15& 18& 21& 23& 26 \\
            3 & 1-2 & $P_7$ & 9 & 12& 14& 17& 19& 22 \\
            3 & 1-2 & $P_8$ & 14 & 7& 9& 12& 14& 16 \\
            3 & 1-2 & $P_9$ & 6 &  3& 5& 7& 9& 11 \\
            3 & 1-2 & $P_10$ & 1 &  1& 2& 3& 4& 5 \\
            3 & 1-2 & $|y_2|$ & 196 &  198& 201& 206& 209& 213 \\
        \end{tabular}
        \caption{GOF: sequence 3 (1)}
        % \label{tab:data}
    \end{table}
\clearpage
\begin{table}[h!]
    \centering
        \begin{tabular}{c| c | c | c | c |c |c |c |c }
            Sequence& timelag & netstat & obs & q0.1 & q0.25 & q0.5 & q0.75 & q0.9 \\
            \hline \hline
            3 & 2-3 & $D_0$ & 11 &  2& 3& 3& 4& 4 \\
            3 & 2-3 & $D_1$ & 11 &  2& 3& 4& 5& 6 \\
            3 & 2-3 & $D_2$ & 12 &  2& 2& 3& 4& 5 \\
            3 & 2-3 & $D_3$ & 9 &  1& 1& 2& 3& 3 \\
            3 & 2-3 & $D_4$ & 2 &  2& 2& 3& 4& 5 \\
            3 & 2-3 & $D_5$ & 1 &  4& 5& 6& 7& 8 \\
            3 & 2-3 & $D_6$ & 0 &  2& 3& 4& 6& 7 \\
            3 & 2-3 & $D_7$ & 2 &  2& 3& 4& 5& 6 \\
            3 & 2-3 & $D_8$ & 1 &  2& 3& 4& 5& 6 \\
            3 & 2-3 & $D_9$ & 0 &  2& 3& 4& 5& 6 \\
            3 & 2-3 & $D_{10}$ & 1 &  1& 2& 3& 4& 5 \\
            3 & 2-3 & $D_{11}$ & 0 &  1& 2& 3& 4& 5 \\
            3 & 2-3 & $D_{12}$ & 0 &  0& 1& 1& 2& 3 \\
            3 & 2-3 & $D_{13}$ & 0 &  0& 0& 0& 1& 2 \\
            3 & 2-3 & $D_{14}$ & 1 &  0& 0& 0& 0& 1 \\
            3 & 2-3 & $D_{15}$ & 1 &  0& 0& 0& 1& 1 \\
            3 & 2-3 & $P_0$ & 36 & 8& 10& 12& 14& 16 \\
            3 & 2-3 & $P_1$ & 26 & 20& 22& 25& 28& 31 \\
            3 & 2-3 & $P_2$ & 4 & 23& 26& 30& 34& 37 \\
            3 & 2-3 & $P_3$ & 0 & 29& 33& 37& 40& 44 \\
            3 & 2-3 & $P_4$ & 1 & 21& 24& 27& 31& 34 \\
            3 & 2-3 & $P_5$ & 0 & 16& 18& 22& 25& 28 \\
            3 & 2-3 & $P_6$ & 0 &  8& 10& 12& 14& 16 \\
            3 & 2-3 & $P_7$ & 1 &  6& 7& 9& 11& 13 \\
            3 & 2-3 & $P_8$ & 0 &  3& 4& 6& 8& 10 \\
            3 & 2-3 & $P_9$ & 0 &  1& 1& 2& 4& 5 \\
            3 & 2-3 & $P_10$ & 0 &  0& 1& 1& 2& 3 \\
            3 & 2-3 & $|y_3|$ & 227 &  180& 183& 187& 190& 193 \\
        \end{tabular}
        \caption{GOF: sequence 3 (2)}
        % \label{tab:data}
    \end{table}
\clearpage
